How Well do we Teach Cybersecurity?\\(Abstract 20 January, Ppaer 27th

### 2018-12-13 ITiCSE2019.tex
More placeholders
Added co-authors
More updates
Add conference dates

\begin{document}
\title{How Well do we Teach Cybersecurity?}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

@@

@@

\subsection{Accreditation}
?AI/TP to write something.

>>>>

\begin{document}
\title{How Well do we Teach Cybersecurity?\\(Abstract 20 January, Ppaer 27th}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\author{Alastair Irons}
\orcid{}
\affiliation{%
  \institution{}
  \streetaddress{}
  \city{} 
  \country{United Kingdom}
}
\email{@lastair.irons@sunderland.ac.uk}

\author{Tom Prickett}
\orcid{}
\affiliation{%
  \institution{}
  \streetaddress{}
  \city{} 
  \country{United Kingdom}
}
\email{tom.prickett@northumbria.ac.uk}

@@

Alastair to write about their Credit Fraud experience (MSc CyberSecurity).
HE Academy grant (to be referenced).

What should be in the general curriculum.

@@

Alastair's experiences.

? Poll CPHC, and/or survey job adverts.
\subsection{Accreditation}
?AI/TP to write something.
